Proposition of a New Experiment to Better Understand the Relation Between Typicality and Prototypes

### 2022-04-24 paper.tex
removed related work section

\section{Related Work}

	In this section we will cover some related work to the topics that are of interest for this paper. In the first section there is an overview on 
	feature extraction methods, in the second section there are prototype construction related work, and in the final section there is an 
	outline of similarity judgment related work.

	\subsection{Feature extraction related work}\label{fes}	
	\subsection{Prototype construction related work}\label{pcs}
	\subsection{Similarity judgment related work}\label{sjs}

>>>>

%\section{Related Work}

%	In this section we will cover some related work to the topics that are of interest for this paper. In the first section there is an overview on 
%	feature extraction methods, in the second section there are prototype construction related work, and in the final section there is an 
%	outline of similarity judgment related work.

%	\subsection{Feature extraction related work}\label{fes}	
%	\subsection{Prototype construction related work}\label{pcs}
%	\subsection{Similarity judgment related work}\label{sjs}
